\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Sean Li-Shin Ho} % Your name
% You can merge both of these into a single line, if you do not have a website.
%\address{+1(123) 456-7890 \\ San Francisco, CA}
\address{+886 975314108 \\ Taoyuan, TW}
\address{\href{mailto:sean.li.shin.ho@gmail.com}{sean.li.shin.ho@gmail.com} \\ \href{https://blog.clam.tw}{blog.clam.tw} \\ \href{sean.li.shin.ho@gmail.com}{sean.li.shin.ho@gmail.com}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

	{Graduated from Master of EarthScience, NCKU\@.  With 2+ years of experience in System Administrators/System Operators/SRE, seeking full-time DevOps/SRE roles.}


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Master of Earth Science}, National Cheng Kung University \hfill {2019 - 2022}\\
Relevant Coursework: Observational Seismology, Programming and Data Processing for EarthScience

{\bf Bachelor of Earth Science}, National Cheng Kung University \hfill {2015 - 2019}
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Technical Skills & Linux, Python, Shell Script, Docker, FreeBSD, CI/CD
\\
Soft Skills & Leadership, Communication\\
%XYZ & A, B, C, D\\
Programming Languages & Python, MATLAB, C/C++, JavaScript, SQL \\
Web Development & Nginx, Flask, Node.js, HTML5, CSS, jQuery, React\\
Cloud Infra \& DevOps & Proxmox VE, Docker, Gitlab CI, GitHub Action, Grafana, Librenms \\
Tools & Git, Unix shell, LaTeX, Vim, Scipy, Numpy, Pandas \\
Cartography Software & GMT, QGIS, Matplotlib \\
\end{tabular}\\
\end{rSection}
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{EXPERIENCE}

%------------------------------------------------

\begin{rSubsection}{Seismology Lab, NCKU}{Jul 2018-Aug 2022}{Research Assistant}{Taiwan}
\item Applying GPS processing result in GIS software for figuring out the relationship between Fault and Soil liquefaction.
\item Developing a seismic data procedure applying to the research.
\item Applyed Python and GMT to visualize the data.
\item Developed a python web application for visualizing the data: \href{https://beachball.clam.moe}{Visualized Focal Mechenism}, to promote Earth science knowledge with web development skills.
\item Used trained model (RED-PAN) to automatically detect micro earthquake event and use relocation methods to figure out relationship between earthquake events.
\item Improved earthquake localization quality through non-linear and relative localization algorithms
\end{rSubsection}

%------------------------------------------------

%\textbf{Role Name} \hfill Jan 2017 - Jan 2019\\
%Company Name \hfill \textit{San Francisco, CA}
% \begin{itemize}
%    \itemsep -3pt {}
%     \item Achieved X\% growth for XYZ using A, B, and C skills.
%     \item Led XYZ which led to X\% of improvement in ABC
%    \item Developed XYZ that did A, B, and C using X, Y, and Z.
% \end{itemize}

\end{rSection}


%----------------------------------------------------------------------------------------
\begin{rSection}{Leadership}


\begin{rSubsection}{Campus Computer \& Network Society at NCKU}{Jul 2018-Jul 2020}{Director and Sysadmin}{}
\item Assisted in configuring, maintaining and upgrading a multi-node virtual machine cluster capable of running 60 to 80 virtual machines, using Proxmox Virtual Environment, an open-source and scalable solution for enterprise.
\item  Established and managed the public mirror for a Linux distribution in NCKU, offering high-speed download services for open-source software packages on campus, improving the effience of developing and deployment of services.
\item Develop and Maintain Bullitin Board System (BBS) for the club: \href{https://term.ccns.cc}{DreamBBS}, serving NCKU students and alumni for the past 27 years, and presented a lecture at the SITCON 2018, and COSCUP 2023.
\item Deployed GitHub Actions for the club's website and BBS, to automate the deployment process and testing procedure.
\end{rSubsection}


\end{rSection}

%------------------------------------------------

\pagebreak

\begin{rSection}{PROJECTS}
%\vspace{-1.25em}

%\begin{rSubsection}{CCNS Anime (React, video.js)}{}{}{}
%\item Designed and developed frontend of anime streaming service using React, Redux, and video.js
%\end{rSubsection}

\begin{rSubsection}{Master Thesis: Investigating Crustal Structures Offshore Tainan through Regional Seismic Signals}{}{}{}
\item Utilized machine learning for waveform picking to identify seismic events with double the accuracy.
\item Improved earthquake localization quality through non-linear and relative localization algorithms. Online seismic source mechanism determination.
\end{rSubsection}
%% 
%% 
\begin{rSubsection}{Online Seismic Source Mechanism Determination}{}{}{}
\item GitHub Repository: \href{https://github.com/sean0921/simplemeca-flask}{sean0921/simplemeca-flask}
\item Developed a Python web service by combining Earth science knowledge with web development skills.
\item Utilized containerization technology for deployment on the Heroku cloud platform, reducing on-site maintenance costs.
\end{rSubsection}
%% 
\begin{rSubsection}{CCNS DreamBBS Project}{}{}{}
\item serving NCKU students and alumni for the past 27 years
\end{rSubsection}
\end{rSection}

%%----------------------------------------------------------------------------------------
%\begin{rSection}{Extra-Curricular Activities}
%\begin{itemize}
%    \item 	Actively write \href{https://www.faangpath.com/blog/}{blog posts} and social media posts (\href{https://www.tiktok.com/@faangpath}{TikTok}, \href{https://www.instagram.com/faangpath/?hl=en}{Instagram}) viewed by over 20K+ job seekers per week to help people with best practices to land their dream jobs.
%    \item	Sample bullet point.
%\end{itemize}
%\end{rSection}

\end{document}
